---
title: "Homework1_Sackler_Summer2020"
author: "Fred LaPolla"
date: "6/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Homework 1

>- Create a list of numbers 1 to 100 and name this list FirstHundred

```{r}

```

>- On your own, explore crusio1 and find the median and mean activity times:

```{r}

```



>- Find summary information about the bodyweights in our mouse data (hint: names(crusio1) will call the names of each column). What is the max value, what is the minimum value.  

```{r}

```

>- Bonus/Challenge: What is the Standard Deviation and skewness of the bodyweight?

```{r}

```


>- Install a package and load, such as "ggplot2" or "dplyr"

```{r}

```


>- What is a directory? How can you look up the current directory in which you are working in R?

```{r}

```


>- How does one read in a CSV file of data into R?

```{r}

```

>- What two commands are needed to install and use a package in R?

```{r}

```

>- What are reasons one would choose to use R for data analysis?

>- When you read in a .csv file into R, what class is the object that you read in (like crusio1)?

>- What command can you use to determine what type of data is in a column?

>- Provide a command to find the type of data in the DX_DBTS column of nyc. 

>- Provide the same command the type of data but use the other way of indexing from what you did above. 

>- In the above Matrix example we made a subset of which columns?

>- What would happen if we had chosen the first 4 columns and made a matrix? What would the class of the cells in this matrix be? Why?

>- If we make a vector,vec<- c(3,9,4,7,8,9), and multiply it by WannaMatrix, what is the value in the third row, third column? 

>- What happens if instead we made a vector vec2 <- c(3,9,4,7,8) and multiply it by WannaMatrix, what is the third row, third column value? What is going on? 


